Adaptive broadcast tree for multicores

### 2013-06-07 graphs/visu_gruyere_binarytree.tex
New visualization applied to all combinations of machines and topologies except for rings

\draw[fill,color=red!10] (-3cm,7.500000mm) rectangle (30cm,-7.500000mm);
\node at (0mm,0mm) {core 00};
\draw[color=black!30] (20mm,0mm) -- (30cm,0mm);
\draw[fill,color=red!10] (-3cm,22.500000mm) rectangle (30cm,7.500000mm);
\node at (0mm,15mm) {core 01};
\draw[color=black!30] (20mm,15mm) -- (30cm,15mm);
\draw[fill,color=red!10] (-3cm,37.500000mm) rectangle (30cm,22.500000mm);
\node at (0mm,30mm) {core 02};
\draw[color=black!30] (20mm,30mm) -- (30cm,30mm);
\draw[fill,color=red!10] (-3cm,52.500000mm) rectangle (30cm,37.500000mm);
\node at (0mm,45mm) {core 03};
\draw[color=black!30] (20mm,45mm) -- (30cm,45mm);
\draw[fill,color=green!10] (-3cm,67.500000mm) rectangle (30cm,52.500000mm);
\node at (0mm,60mm) {core 04};
\draw[color=black!30] (20mm,60mm) -- (30cm,60mm);
\draw[fill,color=green!10] (-3cm,82.500000mm) rectangle (30cm,67.500000mm);
\node at (0mm,75mm) {core 05};
\draw[color=black!30] (20mm,75mm) -- (30cm,75mm);
\draw[fill,color=green!10] (-3cm,97.500000mm) rectangle (30cm,82.500000mm);
\node at (0mm,90mm) {core 06};
\draw[color=black!30] (20mm,90mm) -- (30cm,90mm);
\draw[fill,color=green!10] (-3cm,112.500000mm) rectangle (30cm,97.500000mm);
\node at (0mm,105mm) {core 07};
\draw[color=black!30] (20mm,105mm) -- (30cm,105mm);
\draw[fill,color=blue!10] (-3cm,127.500000mm) rectangle (30cm,112.500000mm);
\node at (0mm,120mm) {core 08};
\draw[color=black!30] (20mm,120mm) -- (30cm,120mm);
\draw[fill,color=blue!10] (-3cm,142.500000mm) rectangle (30cm,127.500000mm);
\node at (0mm,135mm) {core 09};
\draw[color=black!30] (20mm,135mm) -- (30cm,135mm);
\draw[fill,color=blue!10] (-3cm,157.500000mm) rectangle (30cm,142.500000mm);
\node at (0mm,150mm) {core 10};
\draw[color=black!30] (20mm,150mm) -- (30cm,150mm);
\draw[fill,color=blue!10] (-3cm,172.500000mm) rectangle (30cm,157.500000mm);
\node at (0mm,165mm) {core 11};
\draw[color=black!30] (20mm,165mm) -- (30cm,165mm);
\draw[fill,color=orange!10] (-3cm,187.500000mm) rectangle (30cm,172.500000mm);
\node at (0mm,180mm) {core 12};
\draw[color=black!30] (20mm,180mm) -- (30cm,180mm);
\draw[fill,color=orange!10] (-3cm,202.500000mm) rectangle (30cm,187.500000mm);
\node at (0mm,195mm) {core 13};
\draw[color=black!30] (20mm,195mm) -- (30cm,195mm);
\draw[fill,color=orange!10] (-3cm,217.500000mm) rectangle (30cm,202.500000mm);
\node at (0mm,210mm) {core 14};
\draw[color=black!30] (20mm,210mm) -- (30cm,210mm);
\draw[fill,color=orange!10] (-3cm,232.500000mm) rectangle (30cm,217.500000mm);
\node at (0mm,225mm) {core 15};
\draw[color=black!30] (20mm,225mm) -- (30cm,225mm);
\draw[fill,color=red!10] (-3cm,247.500000mm) rectangle (30cm,232.500000mm);
\node at (0mm,240mm) {core 16};
\draw[color=black!30] (20mm,240mm) -- (30cm,240mm);
\draw[fill,color=red!10] (-3cm,262.500000mm) rectangle (30cm,247.500000mm);
\node at (0mm,255mm) {core 17};
\draw[color=black!30] (20mm,255mm) -- (30cm,255mm);
\draw[fill,color=red!10] (-3cm,277.500000mm) rectangle (30cm,262.500000mm);
\node at (0mm,270mm) {core 18};
\draw[color=black!30] (20mm,270mm) -- (30cm,270mm);
\draw[fill,color=red!10] (-3cm,292.500000mm) rectangle (30cm,277.500000mm);
\node at (0mm,285mm) {core 19};
\draw[color=black!30] (20mm,285mm) -- (30cm,285mm);
\draw[fill,color=green!10] (-3cm,307.500000mm) rectangle (30cm,292.500000mm);
\node at (0mm,300mm) {core 20};
\draw[color=black!30] (20mm,300mm) -- (30cm,300mm);
\draw[fill,color=green!10] (-3cm,322.500000mm) rectangle (30cm,307.500000mm);
\node at (0mm,315mm) {core 21};
\draw[color=black!30] (20mm,315mm) -- (30cm,315mm);
\draw[fill,color=green!10] (-3cm,337.500000mm) rectangle (30cm,322.500000mm);
\node at (0mm,330mm) {core 22};
\draw[color=black!30] (20mm,330mm) -- (30cm,330mm);
\draw[fill,color=green!10] (-3cm,352.500000mm) rectangle (30cm,337.500000mm);
\node at (0mm,345mm) {core 23};
\draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
\draw[fill,color=blue!10] (-3cm,367.500000mm) rectangle (30cm,352.500000mm);
\node at (0mm,360mm) {core 24};
\draw[color=black!30] (20mm,360mm) -- (30cm,360mm);
\draw[fill,color=blue!10] (-3cm,382.500000mm) rectangle (30cm,367.500000mm);
\node at (0mm,375mm) {core 25};
\draw[color=black!30] (20mm,375mm) -- (30cm,375mm);
\draw[fill,color=blue!10] (-3cm,397.500000mm) rectangle (30cm,382.500000mm);
\node at (0mm,390mm) {core 26};
\draw[color=black!30] (20mm,390mm) -- (30cm,390mm);
\draw[fill,color=blue!10] (-3cm,412.500000mm) rectangle (30cm,397.500000mm);
\node at (0mm,405mm) {core 27};
\draw[color=black!30] (20mm,405mm) -- (30cm,405mm);
\draw[fill,color=orange!10] (-3cm,427.500000mm) rectangle (30cm,412.500000mm);
\node at (0mm,420mm) {core 28};
\draw[color=black!30] (20mm,420mm) -- (30cm,420mm);
\draw[fill,color=orange!10] (-3cm,442.500000mm) rectangle (30cm,427.500000mm);
\node at (0mm,435mm) {core 29};
\draw[color=black!30] (20mm,435mm) -- (30cm,435mm);
\draw[fill,color=orange!10] (-3cm,457.500000mm) rectangle (30cm,442.500000mm);
\node at (0mm,450mm) {core 30};
\draw[color=black!30] (20mm,450mm) -- (30cm,450mm);
\draw[fill,color=orange!10] (-3cm,472.500000mm) rectangle (30cm,457.500000mm);
\node at (0mm,465mm) {core 31};
\draw[color=black!30] (20mm,465mm) -- (30cm,465mm);
\node at (0mm,480mm) {Machine: gruyere, topology: binarytree};
\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (60mm,0mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (61mm,15mm) {};
\draw[->] (s_0_1.center) -- (r_0_1.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_1_3) at (71mm,15mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_1_4) at (81mm,15mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (71mm,30mm) {};
\draw[->] (s_0_2.center) -- (r_0_2.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_2_6) at (81mm,30mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_2_5) at (91mm,30mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_1_3) at (82mm,45mm) {};
\draw[->] (s_1_3.center) -- (r_1_3.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_3_8) at (92mm,45mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_3_7) at (102mm,45mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_1_4) at (101mm,60mm) {};
\draw[->,very thick,color=red] (s_1_4.center) -- (r_1_4.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_4_9) at (111mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_10) at (121mm,60mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_2_6) at (101mm,90mm) {};
\draw[->,very thick,color=red] (s_2_6.center) -- (r_2_6.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_6_14) at (111mm,90mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_6_13) at (121mm,90mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_2_5) at (111mm,75mm) {};
\draw[->,very thick,color=red] (s_2_5.center) -- (r_2_5.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_5_12) at (121mm,75mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_5_11) at (131mm,75mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_3_7) at (122mm,105mm) {};
\draw[->,very thick,color=red] (s_3_7.center) -- (r_3_7.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_7_15) at (132mm,105mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_7_16) at (142mm,105mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_3_8) at (122mm,120mm) {};
\draw[->,very thick,color=red] (s_3_8.center) -- (r_3_8.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_8_18) at (132mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_17) at (142mm,120mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_9) at (131mm,135mm) {};
\draw[->,very thick,color=red] (s_4_9.center) -- (r_4_9.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_9_19) at (141mm,135mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_9_20) at (151mm,135mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_6_14) at (141mm,210mm) {};
\draw[->,very thick,color=red] (s_6_14.center) -- (r_6_14.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_14_30) at (151mm,210mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_14_29) at (161mm,210mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_10) at (141mm,150mm) {};
\draw[->,very thick,color=red] (s_4_10.center) -- (r_4_10.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_10_22) at (151mm,150mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_10_21) at (161mm,150mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_6_13) at (151mm,195mm) {};
\draw[->,very thick,color=red] (s_6_13.center) -- (r_6_13.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_13_28) at (161mm,195mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_13_27) at (171mm,195mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_5_11) at (151mm,165mm) {};
\draw[->,very thick,color=red] (s_5_11.center) -- (r_5_11.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_11_23) at (161mm,165mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_11_24) at (171mm,165mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_5_12) at (151mm,180mm) {};
\draw[->,very thick,color=red] (s_5_12.center) -- (r_5_12.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_12_26) at (161mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_25) at (171mm,180mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_7_15) at (162mm,225mm) {};
\draw[->,very thick,color=red] (s_7_15.center) -- (r_7_15.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_15_31) at (172mm,225mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_14_30) at (171mm,450mm) {};
\draw[->,very thick,color=red] (s_14_30.center) -- (r_14_30.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_7_16) at (172mm,240mm) {};
\draw[->,very thick,color=red] (s_7_16.center) -- (r_7_16.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_8_18) at (172mm,270mm) {};
\draw[->,very thick,color=red] (s_8_18.center) -- (r_8_18.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_9_19) at (181mm,285mm) {};
\draw[->,very thick,color=red] (s_9_19.center) -- (r_9_19.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_9_20) at (181mm,300mm) {};
\draw[->,very thick,color=red] (s_9_20.center) -- (r_9_20.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_13_28) at (181mm,420mm) {};
\draw[->,very thick,color=red] (s_13_28.center) -- (r_13_28.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_10_22) at (181mm,330mm) {};
\draw[->,very thick,color=red] (s_10_22.center) -- (r_10_22.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_26) at (181mm,390mm) {};
\draw[->,very thick,color=red] (s_12_26.center) -- (r_12_26.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_14_29) at (181mm,435mm) {};
\draw[->,very thick,color=red] (s_14_29.center) -- (r_14_29.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_8_17) at (182mm,255mm) {};
\draw[->,very thick,color=red] (s_8_17.center) -- (r_8_17.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_13_27) at (191mm,405mm) {};
\draw[->,very thick,color=red] (s_13_27.center) -- (r_13_27.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_25) at (191mm,375mm) {};
\draw[->,very thick,color=red] (s_12_25.center) -- (r_12_25.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_11_24) at (191mm,360mm) {};
\draw[->,very thick,color=red] (s_11_24.center) -- (r_11_24.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_11_23) at (191mm,345mm) {};
\draw[->,very thick,color=red] (s_11_23.center) -- (r_11_23.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_10_21) at (191mm,315mm) {};
\draw[->,very thick,color=red] (s_10_21.center) -- (r_10_21.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_15_31) at (192mm,465mm) {};
\draw[->,very thick,color=red] (s_15_31.center) -- (r_15_31.center);

>>>>

\node (core_0_label) at (0mm,0mm) {core 00};
\node (core_1_label) at (0mm,5mm) {core 01};
\node (core_2_label) at (0mm,10mm) {core 02};
\node (core_3_label) at (0mm,15mm) {core 03};
\node (core_4_label) at (0mm,20mm) {core 04};
\node (core_5_label) at (0mm,25mm) {core 05};
\node (core_6_label) at (0mm,30mm) {core 06};
\node (core_7_label) at (0mm,35mm) {core 07};
\node (core_8_label) at (0mm,40mm) {core 08};
\node (core_9_label) at (0mm,45mm) {core 09};
\node (core_10_label) at (0mm,50mm) {core 10};
\node (core_11_label) at (0mm,55mm) {core 11};
\node (core_12_label) at (0mm,60mm) {core 12};
\node (core_13_label) at (0mm,65mm) {core 13};
\node (core_14_label) at (0mm,70mm) {core 14};
\node (core_15_label) at (0mm,75mm) {core 15};
\node (core_16_label) at (0mm,80mm) {core 16};
\node (core_17_label) at (0mm,85mm) {core 17};
\node (core_18_label) at (0mm,90mm) {core 18};
\node (core_19_label) at (0mm,95mm) {core 19};
\node (core_20_label) at (0mm,100mm) {core 20};
\node (core_21_label) at (0mm,105mm) {core 21};
\node (core_22_label) at (0mm,110mm) {core 22};
\node (core_23_label) at (0mm,115mm) {core 23};
\node (core_24_label) at (0mm,120mm) {core 24};
\node (core_25_label) at (0mm,125mm) {core 25};
\node (core_26_label) at (0mm,130mm) {core 26};
\node (core_27_label) at (0mm,135mm) {core 27};
\node (core_28_label) at (0mm,140mm) {core 28};
\node (core_29_label) at (0mm,145mm) {core 29};
\node (core_30_label) at (0mm,150mm) {core 30};
\node (core_31_label) at (0mm,155mm) {core 31};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_1) at (20mm,0mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_2) at (24mm,0mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_1) at (24mm,5mm) {};
\draw[->] ($(s_0_1.east)-(1mm,0mm)$) -- ($(r_0_1.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_1_3) at (28mm,5mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_1_4) at (32mm,5mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_2) at (28mm,10mm) {};
\draw[->] ($(s_0_2.east)-(1mm,0mm)$) -- ($(r_0_2.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_2_6) at (32mm,10mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_2_5) at (36mm,10mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_1_3) at (32mm,15mm) {};
\draw[->] ($(s_1_3.east)-(1mm,0mm)$) -- ($(r_1_3.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_3_8) at (36mm,15mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_3_7) at (40mm,15mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_1_4) at (40mm,20mm) {};
\draw[->,semithick,color=red] ($(s_1_4.east)-(1mm,0mm)$) -- ($(r_1_4.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_9) at (44mm,20mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_10) at (48mm,20mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_2_6) at (40mm,30mm) {};
\draw[->,semithick,color=red] ($(s_2_6.east)-(1mm,0mm)$) -- ($(r_2_6.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_6_14) at (44mm,30mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_6_13) at (48mm,30mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_2_5) at (44mm,25mm) {};
\draw[->,semithick,color=red] ($(s_2_5.east)-(1mm,0mm)$) -- ($(r_2_5.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_5_12) at (48mm,25mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_5_11) at (52mm,25mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_3_7) at (48mm,35mm) {};
\draw[->,semithick,color=red] ($(s_3_7.east)-(1mm,0mm)$) -- ($(r_3_7.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_7_15) at (52mm,35mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_7_16) at (56mm,35mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_3_8) at (48mm,40mm) {};
\draw[->,semithick,color=red] ($(s_3_8.east)-(1mm,0mm)$) -- ($(r_3_8.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_8_18) at (52mm,40mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_8_17) at (56mm,40mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_9) at (52mm,45mm) {};
\draw[->,semithick,color=red] ($(s_4_9.east)-(1mm,0mm)$) -- ($(r_4_9.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_9_19) at (56mm,45mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_9_20) at (60mm,45mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_10) at (56mm,50mm) {};
\draw[->,semithick,color=red] ($(s_4_10.east)-(1mm,0mm)$) -- ($(r_4_10.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_10_22) at (60mm,50mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_10_21) at (64mm,50mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_6_14) at (56mm,70mm) {};
\draw[->,semithick,color=red] ($(s_6_14.east)-(1mm,0mm)$) -- ($(r_6_14.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_14_30) at (60mm,70mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_14_29) at (64mm,70mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_5_11) at (60mm,55mm) {};
\draw[->,semithick,color=red] ($(s_5_11.east)-(1mm,0mm)$) -- ($(r_5_11.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_11_23) at (64mm,55mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_11_24) at (68mm,55mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_5_12) at (60mm,60mm) {};
\draw[->,semithick,color=red] ($(s_5_12.east)-(1mm,0mm)$) -- ($(r_5_12.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_26) at (64mm,60mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_25) at (68mm,60mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_6_13) at (60mm,65mm) {};
\draw[->,semithick,color=red] ($(s_6_13.east)-(1mm,0mm)$) -- ($(r_6_13.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_13_28) at (64mm,65mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_13_27) at (68mm,65mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_7_15) at (64mm,75mm) {};
\draw[->,semithick,color=red] ($(s_7_15.east)-(1mm,0mm)$) -- ($(r_7_15.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_15_31) at (68mm,75mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_14_30) at (68mm,150mm) {};
\draw[->,semithick,color=red] ($(s_14_30.east)-(1mm,0mm)$) -- ($(r_14_30.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_8_18) at (68mm,90mm) {};
\draw[->,semithick,color=red] ($(s_8_18.east)-(1mm,0mm)$) -- ($(r_8_18.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_7_16) at (68mm,80mm) {};
\draw[->,semithick,color=red] ($(s_7_16.east)-(1mm,0mm)$) -- ($(r_7_16.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_26) at (72mm,130mm) {};
\draw[->,semithick,color=red] ($(s_12_26.east)-(1mm,0mm)$) -- ($(r_12_26.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_13_28) at (72mm,140mm) {};
\draw[->,semithick,color=red] ($(s_13_28.east)-(1mm,0mm)$) -- ($(r_13_28.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_9_19) at (72mm,95mm) {};
\draw[->,semithick,color=red] ($(s_9_19.east)-(1mm,0mm)$) -- ($(r_9_19.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_10_22) at (72mm,110mm) {};
\draw[->,semithick,color=red] ($(s_10_22.east)-(1mm,0mm)$) -- ($(r_10_22.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_9_20) at (72mm,100mm) {};
\draw[->,semithick,color=red] ($(s_9_20.east)-(1mm,0mm)$) -- ($(r_9_20.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_14_29) at (72mm,145mm) {};
\draw[->,semithick,color=red] ($(s_14_29.east)-(1mm,0mm)$) -- ($(r_14_29.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_8_17) at (72mm,85mm) {};
\draw[->,semithick,color=red] ($(s_8_17.east)-(1mm,0mm)$) -- ($(r_8_17.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_11_24) at (76mm,120mm) {};
\draw[->,semithick,color=red] ($(s_11_24.east)-(1mm,0mm)$) -- ($(r_11_24.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_10_21) at (76mm,105mm) {};
\draw[->,semithick,color=red] ($(s_10_21.east)-(1mm,0mm)$) -- ($(r_10_21.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_13_27) at (76mm,135mm) {};
\draw[->,semithick,color=red] ($(s_13_27.east)-(1mm,0mm)$) -- ($(r_13_27.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_11_23) at (76mm,115mm) {};
\draw[->,semithick,color=red] ($(s_11_23.east)-(1mm,0mm)$) -- ($(r_11_23.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_25) at (76mm,125mm) {};
\draw[->,semithick,color=red] ($(s_12_25.east)-(1mm,0mm)$) -- ($(r_12_25.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_15_31) at (76mm,155mm) {};
\draw[->,semithick,color=red] ($(s_15_31.east)-(1mm,0mm)$) -- ($(r_15_31.west)+(1mm,0mm)$); 
\begin{pgfonlayer}{background}
\node [fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (s_0_1) (s_0_2) (r_0_1) (s_1_3) (s_1_4) (r_0_2) (s_2_6) (s_2_5) (r_1_3) (s_3_8) (s_3_7) (r_1_4) (s_4_9) (s_4_10) (r_2_6) (s_6_14) (s_6_13) (r_2_5) (s_5_12) (s_5_11) (r_3_7) (s_7_15) (s_7_16) (r_3_8) (s_8_18) (s_8_17) (r_4_9) (s_9_19) (s_9_20) (r_4_10) (s_10_22) (s_10_21) (r_6_14) (s_14_30) (s_14_29) (r_6_13) (s_13_28) (s_13_27) (r_5_11) (s_11_23) (s_11_24) (r_5_12) (s_12_26) (s_12_25) (r_7_15) (s_15_31) (r_14_30) (r_7_16) (r_8_18) (r_9_19) (r_12_26) (r_10_22) (r_9_20) (r_14_29) (r_13_28) (r_8_17) (r_11_24) (r_12_25) (r_11_23) (r_13_27) (r_10_21) (r_15_31) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (s_0_1) (s_0_2) (r_0_1) (s_1_3) (s_1_4) (r_0_2) (s_2_6) (s_2_5) (r_1_3) (s_3_8) (s_3_7) (r_1_4) (s_4_9) (s_4_10) (r_2_6) (s_6_14) (s_6_13) (r_2_5) (s_5_12) (s_5_11) (r_3_7) (s_7_15) (s_7_16) (r_3_8) (s_8_18) (s_8_17) (r_4_9) (s_9_19) (s_9_20) (r_4_10) (s_10_22) (s_10_21) (r_6_14) (s_14_30) (s_14_29) (r_5_11) (s_11_23) (s_11_24) (r_5_12) (s_12_26) (s_12_25) (r_6_13) (s_13_28) (s_13_27) (r_7_15) (s_15_31) (r_14_30) (r_8_18) (r_7_16) (r_12_26) (r_13_28) (r_9_19) (r_10_22) (r_9_20) (r_14_29) (r_8_17) (r_11_24) (r_10_21) (r_13_27) (r_11_23) (r_12_25) (r_15_31)] (allobjects) {};
